%-------------------------
% Resume in Latex
% Based on: https://github.com/wilmeragsgh/resume/
% requires: sudo apt install texlive-full
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
  \vspace{1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands

\newcommand{\sepsection}{\vspace{25pt}}

\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
 \underline{#1:} #2
}

% COLOR THEMES SELECTION
\colorlet{textcolor}{black}
\colorlet{urlcolor}{red}

\begin{document}

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Abel A. Mengistu} & \href{tel:202-492-4738}{\color{urlcolor}{\faicon{phone}} \color{textcolor}  202-492-4738} \\
  Software Developer & \href{mailto:mengistu.abel@gmail.com}{\color{urlcolor}{\faicon{envelope}} \color{textcolor} mengistu.abel@gmail.com} \\
  \textsl{District Of Columbia, USA} & \href{https://github.com/abeloof}{  \color{urlcolor}{\faicon{github}} \color{textcolor} www.github.com/abeloof}
\end{tabular*}
% ---

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland, Baltimore County}{Baltimore, MD}
      {B.Sc in Information Systems}{Jan. 2009 -- Aug. 2011}
    \resumeSubheading
      {Montogomery College}{Takoma Park, MD}
      {A.A in Computer Information Systems (transfered)}{June 2006 -- Dec. 2008}  
  \resumeSubHeadingListEnd
% CERTIFICATIONS
\section{Certifications}
  \resumeSubHeadingListStart
  \resumeSubheading
      {@ University of Maryland, Baltimore County}{}
      {Network Administration Certificate}{Issued on August 2011}
    \resumeSubheading
      {@ Microsoft}{}
      {\href{https://learn.microsoft.com/api/credentials/share/en-us/AbelM-7089/2CD8D55E67CA05CE?sharingId=1EAA6EDBC20E2089}{Microsoft Certified: Azure Developer Associate}}{Expires on October 2025}
  \resumeSubHeadingListEnd
% ---
% PROGRAMMING SKILLS
\section{Technical skills}
  \resumeSubHeadingListStart
  
  \resumeSubItem{\textbf{Programming languages:} C\#, .NET Framework, .NET 5+, Typescript, Javascript, VB, HTML, CSS}
  
  \resumeSubItem{\textbf{Cloud services:} AWS (Lambda, S3), GCP (Storage), Azure (Blob/Table storage, CosmosDB, Functions, AppService, Queues, ServiceBus, EventHub, Durable Functions).}
  
  \resumeSubItem{\textbf{UI frameworks:} AngularJs, Angular, ReactJs}
  
  \resumeSubItem{\textbf{Others:} Docker, Kubernetes, Powershell, Python, C, Java}
  
  \resumeSubHeadingListEnd

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {GreenDot Corporation}{(remote) DC, USA}
      {Sr. Software Engineer}{October 2021 - February 2024}
      \resumeItemListStart
      \resumeItem{Participated in daily agile scrum meetings, collaborating with cross-functional teams from US and China to design, develop, and successfully implement new features, and resolve production bugs for banking-as-a-service(baas) platform.}
      \resumeItem{Closely collaborated with product and quality assurance teams to gather requirements, design system specifications, create feature acceptance test cases, and deliver a well-designed and thoroughly tested microservice applications.}
      \resumeItem{Served as a key member of the core team that transitioned GreenDot's payment systems to new payment processor using microsoft azure; created an initial proof-of-concept for azure functions, azure durable functions, azure appservice authentications, and provided support to other teams as needed when production issues arose.}
      \resumeItem{Documented and generated various BPMN 2.0 compliant software process models and further refined the same modles to document and generate expected software system updates and upgrades. }
      \resumeItemListEnd
      \resumeTech{Technologies}{aws, azure, git, perforce, teamcity, c\#, .net 6, datadog, sonarqube, powershell, rabbitmq, cassandra, redis, activebatch, elasticsearch, ms-sql, docker, linux}\\   
    \resumeSubheading
      {Motions Recruitment}{Arlington, VA}
      {Sr. Net Developer}{February 2020 - June 2020}
      \resumeItemListStart
      \resumeItem{Participated in developing, maintaining, and upgrading a cloud native healthcheck-as-a-service(haas) web application for internal development teams.}
      \resumeItem{Integrated existing angular \& asp.net core applications with azure ad to allow single-sign-on (sso) and give role based access to exisiting api resources.}
      \resumeItemListEnd
      \resumeTech{Technologies}{azure, c\#, .net core, .net standard, asp.net, azure devops, typescript, angular, ms-sql, redis, signalr, docker, linux }\\
    \resumeSubheading
      {Evolent Health}{Arlington, VA}
      {Sr. Software Engineer}{February 2016 - January 2019}
      \resumeItemListStart
      \resumeItem{Participated in daily and weekly agile scrum ceremonies, including planning, grooming, and daily stand-ups, to drive the development, maintenance, and implementation of new features for a software-as-a-service healthcare web application.}
      \resumeItem{Participated in sdlc process, including requirement gathering, design and documentation, implementation, unit testing, conducting code reviews, updating continuous integration and delivery pipelines, and supporting post-production deployment bug fixes, to enhance and add new features to existing Evolent Health’s Identifi platform.}
      \resumeItem{Participated in platform redesign effort by refactoring and adding proper caching strategy to existing web api resources which improved overall application performace and scalability.}
      \resumeItem{Designed relational database tables to store normalized data, created or added new indexes to imporve data read operations, and wrote stored procedures to improve data write operations performace.}
      \resumeItem{Designed and implemented a dynamic pdf document generator using aspose.net which allowed end users to generate adhoc reports and send an efax  on demand.}
      \resumeItemListEnd
      \resumeTech{Technologies}{azure, c\#, .net core, .net standard, asp.net, vsts, git, teamcity, elk, javascript, nodejs, angularjs, ms-sql, sonarqube, redis, rabbitmq, masstransit, docker, linux }\\
    \resumeSubheading
      {Matrix Group International}{Crystal City, VA}
      {Web Developer}{April 2015 - September 2015}
      \resumeItemListStart
      \resumeItem{Maintained and enhanced sitefinity based web applications, used internally by employees of professional associations and their members.}
      \resumeItem{Developed custom sitefinity modules and api's, enabling seamless data access and storage for customized dynamic client-side sitefinity pages.}
      \resumeItemListEnd
      \resumeTech{Technologies}{c\#, .net framework, php, tfs, teamcity, javascript, angularjs, ms-sql, redis, iis, sitefinity, jira }\\
    \resumeSubheading
      {Towers Watson}{Arlington, VA}
      {Software Developer}{April 2014 - March 2015}
      \resumeItemListStart
      \resumeItem{Maintained, upgraded, and implemented new client-specific pension plan features for a software-as-a-service(saas) benefit administration web application.}
      \resumeItem{Coordinated with multiple project and client team members to develop and deliver, a fully tested custom pension administration web applications.}
      \resumeItem{Wrote and optimized stored procedure \& sql scripts to extract unique data for dynamic reports.}
      \resumeItem{Took on various roles per project; tech lead, pension calculator developer (c\# or c), all other developer (ui, api resources \& sql) and izenda reports developer (sql).}
      \resumeItemListEnd
      \resumeTech{Technologies}{c\#, c, vb, asp, .net framework, redgate ci, vsts/tfs, javascript, angularjs, ms-sql, redis, iis }\\
    \resumeSubheading
      {DealerOn Inc}{Rockville, MD}
      {Software Developer}{May 2013 - April 2014}
      \resumeItemListStart
      \resumeItem{Participated in daily kanban production software releases which included production bug fixes, platform improvement and new feature roll outs for a software-as-a-service automotive content relational and inventory management web applications.}
      \resumeItem{Worked closely with account managers and production managers to generate various system change specifications document.}
      \resumeItemListEnd
      \resumeTech{Technologies}{c\#, vb, python, asp, .net framework, teamcity, tfs, mercurial-scm/tortoisehg, javascript, angularjs, ms-sql, redis, iis, jira }\\   
\resumeSubHeadingListEnd
% ---

% PROJECTS
\section{Personal Projects / Hobbies}

  \resumeSubHeadingListStart
    \resumeSubItem{Homelab: personal cloud} \\
    \resumeSubItem{Soccer} \\
    \resumeSubItem{Cooking} \\
  \resumeSubHeadingListEnd
% ---

\end{document}
